High-Dimensional Regularized Discriminant Analysis

### 2016-01-02 reports/paper-hdrda.Rnw
Updated Discussion section

We have compared our proposed \emph{HDRDA} classifier to several recently
proposed classifiers, including the Dudoit, Pang, Tong, and Guo classifiers,
each of which assumes independence of the features conditional on class
membership. Despite the rapid computational performance of diagonal classifiers
and the reduction in the number of parameters to estimate, \cite{Mai:2012bf} and
\cite{Fan:2012iq} have noted that diagonal classifiers can often yield inferior
classification performance to other classification methods. We have shown that
the \emph{HDRDA} classifier often yields superior classification accuracy to the
diagonal classifiers considered, confirming the assertions of \cite{Mai:2012bf}
and \cite{Fan:2012iq}. Furthermore, the implementation of
\eqref{eq:hdrda-decomposed} in the {\tt sparsediscrim} R package was comparable
to that of the diagonal classifiers in terms of computational runtime. Moreover,
when preliminary variable selection was applied to the data in our
classification study, the time to perform model selection with our proposed
classifier was nearly instantaneous. Hence, our proposed \emph{HDRDA} classifier
is competitive in terms of classification accuracy for modern small-sample,
high-dimensional data sets and requires substantially less computing time than
standard regularized classifiers, such as regularized discriminant analysis
proposed by \cite{Friedman:1989tm}.

Given the \emph{RDA} classifier has been shown to have excellent performance in
the high-dimensional setting \citep{Webb:2011vu} but is limited by its
computationally intense model selection procedure, our work enables the
\emph{RDA} classifier to be employed with small-sample, high-dimensional data in
practice. This is reassuring because the \emph{RDA} classifier remains widely
popular in the literature. In fact, variants of the RDA classifier have been
applied to microarray data \citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te},
facial recognition
\citep{Ching:2012fu,Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we},
handwritten digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep{Wu:1996us,Aeberhard:1993fp}.

@@

Despite the claims of \cite{FernandezDelgado:2014ul} that the random forest
classifier is typically superior, we observed that the classifiers designed for
high-dimensional data were indeed superior.

>>>>

We have compared our proposed \emph{HDRDA} classifier to the random-forest and
Witten classifiers as well as the Pang, Tong, and Guo classifiers, each of which
assumes independence of the features conditional on class membership. Despite
the rapid computational performance of diagonal classifiers and the reduction in
the number of parameters to estimate, \cite{Mai:2012bf} and \cite{Fan:2012iq}
have noted that diagonal classifiers can often yield inferior classification
performance to other classification methods. We have shown that the \emph{HDRDA}
classifier often yields superior classification accuracy to the diagonal
classifiers considered when applied to small-sample, high-dimensional data sets,
confirming the assertions of \cite{Mai:2012bf} and \cite{Fan:2012iq}.
Furthermore, we have demonstrated that \emph{HDRDA} classifiers are more robust
to the presence of outliers than the diagonal classifiers.

We also considered the popular penalized linear discriminant analysis from
\cite{Witten:2011kc} because it was specifically designed for high-dimensional
gene-expression data. We had expected its classification performance to be
competitive within our classification study and perhaps superior. Contrarily,
its underperformance in our empirical studies show that it is sensitive to
outliers and unable to achieve comparable results with other classifiers
designed for small-sample, high-dimensional data. Also, despite the claims of
\cite{FernandezDelgado:2014ul} that the random forest classifier is typically
superior to other classifiers, we observed that the random-forest classifier was
indeed competitive but was typically outperformed by classifiers developed for
small-sample, high-dimensional data.

The \emph{HDRDA} implementation of \eqref{eq:hdrda-decomposed} in the {\tt
  sparsediscrim} R package was comparable to that of the diagonal classifiers in
terms of computational runtime. Given the \emph{RDA} classifier from
\cite{Friedman:1989tm} has been shown to have excellent performance in the
high-dimensional setting \citep{Webb:2011vu} but is limited by its
computationally intense model selection procedure, our work enables the
\emph{RDA} classifier to be employed with small-sample, high-dimensional data in
practice. This is reassuring because the \emph{RDA} classifier remains widely
popular in the literature. In fact, variants of the RDA classifier have been
applied to microarray data \citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te},
facial recognition
\citep{Ching:2012fu,Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we},
handwritten digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep{Wu:1996us,Aeberhard:1993fp}.

@@
